%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Program Committees}


\begin{cventries}

% ---------------------------------------------------------
\cvmultientry
{Johnson Controls} % Organization
{Montreal, QC}
{Jan. 2008 - Jan. 2020} % Dates
{
%---------------------------------------------------------
\cvsubentry
{Lead Principal Research Engineer} % Job title
{} % Location
{Oct. 2011 - Jan. 2018} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Initiated and conducted research on control algorithms and fault detection and diagnostic techniques to improve the energy efficiency of heating, ventilating and air-conditioning (HVAC) systems in buildings.}
\item {Responsible for development of Modelica-based dynamic HVAC system models and use of models for development of control algorithms and diagnostic tools.}
\item {Initiated and guided university research collaborations supporting internal technology priorities.}
\item {Provided industry outreach and technical guidance for research projects funded by ASHRAE and U.S. Department of Energy.}
\end{cvitems}
}
%---------------------------------------------------------
\cvsubentry
{Principal Research Engineer} % Job title
{} % Location
{Jan. 2008 - Oct. 2011} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Collaborated with research colleagues to develop and test algorithms for integrated control and fault detection, model-based economizer control and optimal start.}
\item {Developed simulation platforms using Matlab, Simulink, Energy Plus, and Modelica-based tools and libraries to aid development and testing of control and fault detection algorithms.}
\end{cvitems}
}
}

%---------------------------------------------------------
\end{cventries}
