%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% ---------------------------------------------------------
\cvmultientry
{Johnson Controls} % Organization
{Montreal, QC}
{Jan. 2008 - Jan. 2020} % Dates
{
%---------------------------------------------------------
\cvsubentry
{Lead Principal Research Engineer} % Job title
{} % Location
{Oct. 2011 - Jan. 2018} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Initiated and conducted research on control algorithms and fault detection and diagnostic techniques to improve the energy efficiency of heating, ventilating and air-conditioning (HVAC) systems in buildings.}
\item {Responsible for development of Modelica-based dynamic HVAC system models and use of models for development of control algorithms and diagnostic tools.}
\item {Initiated and guided university research collaborations supporting internal technology priorities.}
\item {Provided industry outreach and technical guidance for research projects funded by ASHRAE and U.S. Department of Energy.}
\end{cvitems}
}%
%---------------------------------------------------------
\cvsubentry
{Principal Research Engineer} % Job title
{} % Location
{Jan. 2008 - Oct. 2011} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Collaborated with research colleagues to develop and test algorithms for integrated control and fault detection, model-based economizer control and optimal start.}
\item {Developed simulation platforms using Matlab, Simulink, Energy Plus, and Modelica-based tools and libraries to aid development and testing of control and fault detection algorithms.}
\end{cvitems}
}
}
%---------------------------------------------------------
\cventry
{Natural Resources Canada} % Organization
{Varennes, QC} % Location
{Jan. 2005 - Jan. 2008} % Date(s)
{Secondment Assignment from the Iowa Energy Center} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed research plans and established collaborative research projects for Intelligent Buildings Group.}
\item {Conducted research on controls and diagnostics for HVAC and supermarket refrigeration systems.}
\end{cvitems}
}
%---------------------------------------------------------
\cventry
{Iowa Energy Center} % Organization
{Ankeny, IA} % Location
{Nov. 2000 - Jan. 2008} % Date(s)
{Research Engineer} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Lead technical researcher of the National Building Controls Information Program.}
\item {Conducted sponsored research and demonstration projects, and supported IEC funded research, related to building controls, fault detection and diagnostics, and commissioning for private industry and federal government.}
\item {Represented the Iowa Energy Center on national initiatives, collaborations and committees related to building energy efficiency.}
\item {Provided technical support and guidance for IEC-funded research projects.}
\end{cvitems}
}%
%---------------------------------------------------------
\cventry
{National Institute of Standards and Technology} % Organization
{Gaithersburg, MD} % Location
{Oct. 1994 - Nov. 2000} % Date(s)
{Principal Investigator / Project Leader} % Job title
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Conducted research related to the development and testing of fault detection and diagnostic (FDD) methods for HVAC systems. Led the development of APAR (Air-handling unit Performance Assessment Rules).}
\item {Collaborated with staff at Johnson Controls, Inc. to perform simulation and laboratory testing of advanced control strategies and FDD methods.}
\item {Participated in international collaborations to perform FDD research with the Korea Institute of Energy Research, the Scientific and Technical Building Centre in Paris, France, and members of the International Energy Agency (IEA) Annex 34 working group.}
\item {Monitored sponsored research on FDD methods for rooftop units conducted at Purdue University.}
\item {Served as the IEA Annex 34 country representative for the United States.}
\end{cvitems}
}
\end{cventries}
